% \subsection{Reinforcement Learning for Dexterous Grasping}
% Reinforcement learning (RL) has emerged as a powerful paradigm for acquiring
% complex manipulation skills in high-degree-of-freedom (DoF) systems such as
% dexterous robotic hands. Recent research has relied heavily on model-free RL
% algorithms, including DDPG, SAC, and PPO, which have demonstrated strong
% performance in learning a variety of skills across a wide range of robotic
% setups.

% GraspXL reformulates the RL problem as an objective-conditioned
% motion generation task. The policy is trained to simultaneously
% produce stable grasps while satisfying user-specified motion
% objectives, such as graspable regions defined via signed
% distance fields (SDFs), approach directions, wrist rotations,
% and target hand poses. This formulation enables multi-objective
% policy learning within a unified reinforcement learning
% framework.

% DextrAH-RGB\cite{singh2024dextrah} adopts a geometric fabrics-based reinforcement
% learning framework, in which the policy operates within a
% hand-designed fabric-induced action manifold. This structured
% representation effectively reduces the action-space dimension
% and significantly simplifies reward design during training.

\textbf{Skill Distillation.} Skill distillation transfers behavior from a high-capacity teacher to a compact student and has been adopted from
vision to robotics. In robotics, the teacher can leverage privileged state and simulator access during training,
while the student is distilled to operate from on-board observations (e.g., RGB). DexTrAH-RGB~\cite{singh2024dextrah} 
distills a privileged RL teacher into an RGB-based policy via DAgger-based imitation learning, while 
UniGraspTransformer~\cite{wang2025unigrasptransformer} distills offline trajectories from object-specific teachers 
into a unified Transformer policy.

\textbf{Interactive Imitation Learning.} Many imitation learning methods operate offline, using a fixed dataset of expert demonstrations to match the expert
action distribution~\cite{zhang2025contactdexnet,zhang2025omnidexvlg}. In sequential decision-making, however,
distributional shift induces covariate shift and compounding errors. Interactive imitation learning\cite{welte2025interactive} mitigates this
issue by collecting supervision online under the learner-induced state distribution.

DAgger\cite{ross2011reduction} addresses covariate shift by iteratively rolling out the learner and relabeling visited
states with an expert, thereby aggregating data under the learner-induced state distribution. SafeDAgger\cite{zhang2016query} extends
DAgger with a teacher-intervened rollout policy that takes over in high-risk states to reduce unsafe exploration.
Recent variants \cite{hoque2021lazydagger,hoque2021thriftydagger} extend interactive imitation learning to robotic manipulation, yet often rely on human
supervision. Fully autonomous expert relabeling during online distillation remains rare in robotic manipulation,
especially for dexterous, contact-rich tasks.

\textbf{Vision-Language-Guided Robot Learning.}
Visual and semantic information is widely recognized as a strong 
cue for embodied agents to interpret task specifications and reason 
about unstructured environments~\cite{firoozi2025foundation,han2026multimodal}.
Some methods use VLMs to generate demonstrations or supervisory signals for
offline policy construction~\cite{duan2025manipulate,duan2024aha}. Other
approaches invoke VLMs at execution time for trajectory generation, failure
recovery, or policy steering while keeping the underlying policy
fixed~\cite{huang2023voxposer,dai2025racer,wu2025foresight}.
